---
title: 'Logistic Regression: Pima Indians Diabetes Dataset'
author: "Sophia Yap"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

# Regression

Regression is a broad statistical idea used to examine relationships between an outcome variable and one or more predictor variables.

Some common types of regression include:

- **Simple linear regression**
- **Multiple linear regression**
- **Logistic regression**

Logistic regression is used when the outcome variable has **two possible categories**, such as yes/no, success/failure, or diabetes/no diabetes.

# Pima Indians Diabetes Dataset

In this example, we use the Pima Indians Diabetes dataset. The outcome variable indicates whether a person has diabetes.

We will use **glucose** and **age** as predictor variables.

## Import the Data

First, we load the dataset from GitHub.

```{r}
url <- "https://raw.githubusercontent.com/jbrownlee/Datasets/master/pima-indians-diabetes.data.csv"

PimaIndiansDiabetes <- read.csv(url, header = FALSE)

head(PimaIndiansDiabetes)
```

## Rename the Variables

The original dataset does not contain column names, so we assign meaningful names to the variables.

```{r}
names(PimaIndiansDiabetes) <- c(
  "pregnant",
  "glucose",
  "pressure",
  "triceps",
  "insulin",
  "mass",
  "pedigree",
  "age",
  "diabetes"
)

head(PimaIndiansDiabetes)
```

## Examine the Structure of the Data

We can use `str()` to examine the structure and data types of the variables.

```{r}
str(PimaIndiansDiabetes)
```

# Logistic Regression Model

We fit a logistic regression model using `glm()`.

The outcome variable is **diabetes**, and the predictor variables are **glucose** and **age**.

```{r}
model <- glm(
  diabetes ~ glucose + age,
  data = PimaIndiansDiabetes,
  family = binomial()
)

summary(model)
```

# Interpretation

### Outcome

The outcome variable is **diabetes**, which indicates whether the person has diabetes.

### Predictors

The predictors in the model are:

- **Glucose**
- **Age**

### Results

The logistic regression results can be interpreted in terms of the **odds of diabetes**.

A positive coefficient for **glucose** indicates that higher glucose levels are associated with higher odds of diabetes, while holding age constant.

A positive coefficient for **age** indicates that increasing age is associated with higher odds of diabetes, after accounting for glucose.

Therefore, in this model, **glucose and age have positive associations with the odds of diabetes**.
