---
title: "Multiple Regression"
author: "Sophia Yap"
date: "2026-10-03"
output: pdf_document
---

# Regression

Regression is the broad idea, and simple linear regression, multiple linear regression, and logistic regression are different types of regression models.

- **Simple linear regression** has one predictor and one outcome.
- **Multiple linear regression** has several predictors and one outcome.
- **Logistic regression** is used when the outcome is categorical, usually binary.

In multiple regression, we use several predictors to explain or predict one outcome.

# Example 1: Trees

We will use the built-in `trees` dataset.

## Data Visualisation

```{r}
library(ggplot2)

data(trees)

trees |>
  ggplot(aes(Girth, Volume, color = Height)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  labs(
    title = "Tree Volume Explained by Girth and Height",
    x = "Girth",
    y = "Volume",
    color = "Height"
  )
```

## Model

We can use multiple linear regression to model tree volume using girth and height as predictors.

```{r}
model <- lm(Volume ~ Girth + Height, data = trees)

summary(model)
```

## Interpretation

Girth and height are associated with an increase in tree volume.

The regression coefficients show the expected change in tree volume associated with each predictor while holding the other predictor constant.

# Example 2: Penguins

We will use the `penguins` dataset from the `palmerpenguins` package.

## Data Visualisation

```{r}
library(palmerpenguins)

penguins |>
  ggplot(aes(bill_depth_mm, bill_length_mm)) +
  geom_point(aes(color = species), alpha = 0.7) +
  geom_smooth(
    aes(color = species),
    method = "lm",
    se = FALSE
  ) +
  theme_bw() +
  labs(
    title = "Penguin Bill Length Explained by Bill Depth",
    x = "Bill Depth",
    y = "Bill Length"
  )
```

## Model

We can use multiple linear regression to model bill length using bill depth and species as predictors.

```{r}
model2 <- lm(
  bill_length_mm ~ bill_depth_mm + species,
  data = penguins
)

summary(model2)
```

## Interpretation

Approximately **79% of the variation in bill length** can be explained by bill depth and species, based on the R-squared value.

Using **Adelie** as the reference species:

* Changing from Adelie to Chinstrap is associated with an estimated increase of **9.939 mm** in bill length, holding bill depth constant.
* Changing from Adelie to Gentoo is associated with an estimated increase of **13.4 mm** in bill length, holding bill depth constant.

# Summary

Multiple linear regression allows us to examine the relationship between an outcome variable and several predictors.

In these examples:

* **Trees:** Volume is the outcome, while Girth and Height are the predictors.
* **Penguins:** Bill Length is the outcome, while Bill Depth and Species are the predictors.

```
```

