---
title: "Simple Linear Regression"
author: "Sophia Yap"
date: "2026-10-03"
output: pdf_document
---

# Regression

Regression is the broad idea, and simple linear regression, multiple linear
regression, and logistic regression are different types/models.

Simple linear regression only has one predictor.

## Data and plot

```{r}
library(ggplot2)

head(women)

women |>
  ggplot(aes(height, weight)) +
  geom_point(size = 3, alpha = .5) +
  geom_smooth(method = lm, se = FALSE) +
  theme_bw() +
  labs(
    title = "Weight explained by Height in Women",
    x = "Height",
    y = "Weight"
  )
```

## Linear model

A linear model asks: How much of the change in weight can be explained by
change in height?

```{r}
model1 <- lm(weight ~ height, data = women)

summary(model1)
```

The slope is approximately 3.45. This means that for every one-unit increase
in height, the predicted weight increases by approximately 3.45 units.

The R-squared is approximately 0.991, meaning that about 99.1% of the
variation in weight is explained by height in this linear model.